\documentclass[letter, 11pt]{article}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
\thispagestyle{empty}
\begin{document}

\textheight=11in
\flushleft

\LARGE\textbf{Curriculum Vitae \hspace{6.8cm} Anthea Cheung\\} \vspace{-1.65cm}

\vspace{2.5cm}


\Large \textbf{Education} \vspace{0.3cm}\\
\large \textbf{Boston University}\\
MA in Mathematics, 2015\\
PhD. student in Mathematics, 2013- present
\vspace{0.4cm}\\

\large \textbf{Wellesley College} \\
B.A. in Mathematics, minor in Computer Science, May 2012.\\
Phi Beta Kappa, \textit{magna cum laude}.
\vspace{0.4cm}\\

\Large \textbf{Experience}\vspace{0.4cm}\\

\parbox[l]{\textwidth}{
\large \textbf{Boston University Mathematics Department} \makebox[3in][r]{\small Boston, MA; 2013-present}
\textit{Teaching Fellow- }Led weekly discussions to help students understand material that are introduced in lecture. Provided one-on-one assistance to students during office hours. Worked with other teaching fellows and faculty members to organize and grade exam materials. 
}
\vspace{0.4cm}\\
\large \textbf{Program in Mathematics for Young Scientists}\makebox[3.1in] [r]{\small Boston, MA; Summer 2014, 2015}
\textit{T$^2$- }
Guided middle school and high school teachers in completing daily problem sets on number theory. Encouraged participants to actively engage with mathematical concepts. Assessed participants' progress and aided program director in creating an immersive environment for creative mathematical dialogue.

  \vspace{0.4cm}\\
\parbox[l]{\textwidth}{
\large \textbf{Nuance Communications} \makebox[4.6in][r]{\small Cambridge, MA; 2012-2013}
\textit{Natural Language Processing Research Engineer- } Developed and supporting natural language understanding technology for advanced multilingual spoken language applications. Trained machine learning tools to process user data. Analyzed language models to find solutions to accuracy issues, and supported research scientists in maintaining software tools.  
}
\vspace{0.4cm}\\

\parbox[l]{\textwidth}{
\large \textbf{ID$^3$} \makebox[6.5in][r]{\small Cambridge, MA; Summer 2012}
\textit{Project Consultant- }
Conducted analysis of an economic model of stakeholders and actors in personal data marketplace. Assisted in developing a simulation for running scenarios, testing hypotheses, and developing policy suggestions for the big data economy.
}
\vspace{0.4cm}\\

\Large \textbf{Publications}
\vspace{0.4cm}\\
\normalsize
Ding Liu, \textbf{Anthea Cheung}, Anna Margolis, Patrick Redmond, Jun-won Suh, Chao Wang: Data driven methods for utterance semantic tagging. INTERSPEECH 2013: 2068-2070.
\vspace{0.4cm}\\

\Large \textbf{Skills and Interests}
\vspace{0.4cm}\\
\normalsize
\begin{itemize}
\item Knowledge of Java, Python, and R.
\item Fluent in English, Cantonese, and Mandarin. Proficient in French.
  
\end{itemize}


\end{document}
